---
title       : Trustworthiness of Information across Information Domains
subtitle    : The "Factiness" of Information
author      : MJ Cho
job         : Cyber Social Mini Conference
logo        : stanford.gif
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
output      : pdf
---

```{r echo=FALSE}
# code chunk to load libraries and data
library(ggplot2)
library(gridExtra)
load("statsList.rda")
load("topicsDF.rda")
load("topicAndTerm.rda")
load("DFhr.rda")
```

## Information Trustworthiness
>- An open research question!
>- 1. Database, machine learning, and natural language understanding
  - data/knowledge fusion
  - data veracity and source credibility
>- 2. Computational journalism 
  - automated fact-checking: also an engineering question?
  - combining currently available tools vs. "fundamental breakthroughs in multiple fronts"

---

## Factiness, Truthiness
>- 1. True/False value of a claim is importent, but...
  - It's not only about fact; it's also about the possiblity of having some "facts"
  - Nathan Jurgenson: "The facts of Obama’s birthplace mattered less..."
>- 2. Facts vs. "facty" info
  - "Factiness is the taste for the feel and aesthetic of 'facts'" 
  - We like to be informed, like, super informed: "facty" info is attractive whether it true or not

---

## Cyber Social Project and Information Trustworthiness
>- 1. Consumer-side media diet
  - Info presented vs. Info consumed
>- 2. Moment-by-moment granularity
  - Naturally-occurring data
>- 3. Duke Database Research Group's ClaimBuster
  - SVM trained on presidential debate texts
  - Has a REST API

---

## Factiness by Behavioral Categories
```{r echo=FALSE,warning=FALSE,fig.align='center',fig.width=14}
c1 <- ggplot(statsList[[1]], aes(x = category, y = avg, fill = category)) + 
  geom_bar(position = position_dodge(), stat = "identity",
           width = .8) +
  geom_errorbar(aes(ymin = lowerCI, ymax = upperCI),
                width = .1, position = position_dodge(.9)) +
  ggtitle("Mean Factiness Score by Behavioral Category, Phone") + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
c2 <- ggplot(statsList[[2]], aes(x = category, y = avg, fill = category)) + 
  geom_bar(position = position_dodge(), stat = "identity",
           width = .8) +
  geom_errorbar(aes(ymin = lowerCI, ymax = upperCI),
                width = .1, position = position_dodge(.9)) +
  ggtitle("Mean Factiness Score by Behavioral Category, Laptop") + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
grid.arrange(c1, c2, nrow = 1)
```

---

## Topic Modeling and Trend of the Mean Factiness Score: Phone
```{r echo=FALSE,warning=FALSE,fig.align='center',fig.width=10}
ph1 <- ggplot(phTopicsDF, aes(hour, fill = phAll.term[phTopics])) + 
  geom_density(position = "stack") + 
  scale_fill_discrete(name = "Topic Categories") + 
  ggtitle("LDA Topic Modelling: Phone")
ph2 <- ggplot(phTopicsDF, aes(hour, score)) + 
  geom_smooth(method = "loess", span = 0.4)
grid.arrange(ph1, ph2, ncol = 1)
```

---

## Topic Modeling and Trend of the Mean Factiness Score: Laptop
```{r echo=FALSE,warning=FALSE,fig.align='center',fig.width=10}
la1 <- ggplot(laTopicsDF, aes(hour, fill = laAll.term[laTopics])) + 
  geom_density(position = "stack") + 
  scale_fill_discrete(name = "Topic Categories") + 
  ggtitle("LDA Topic Modelling: Laptop")
la2 <- ggplot(laTopicsDF, aes(hour, score)) + 
  geom_smooth(method = "loess", span = 0.4)
grid.arrange(la1, la2, ncol = 1)
```

---

## Trend of the Mean Factiness Score, 10-11 am: Phone
```{r echo=FALSE,warning=FALSE,fig.align='center',fig.width=10}
phTopicsDF.hr <- phTopicsDF[ph.timeInt, ]
ph1 <- ggplot(phTopicsDF.hr, aes(time, fill = phAll.term[phTopics[ph.timeInt]])) + 
  geom_density(position = "stack") + 
  scale_fill_discrete(name = "Topic Categories") + 
  ggtitle("LDA Topic Modelling: phone")
ph2 <- ggplot(phTopicsDF.hr, aes(time, score)) + 
  geom_smooth(method = "loess", span = 0.1)
grid.arrange(ph1, ph2, ncol = 1)
```

---

## Trend of the Mean Factiness Score, 10-11 am: Laptop
```{r echo=FALSE,warning=FALSE,fig.align='center',fig.width=10}
laTopicsDF.hr <- laTopicsDF[la.timeInt, ]
la1 <- ggplot(laTopicsDF.hr, aes(time, fill = laAll.term[laTopics[la.timeInt]])) + 
  geom_density(position = "stack") + 
  scale_fill_discrete(name = "Topic Categories") + 
  ggtitle("LDA Topic Modelling: laptop")
la2 <- ggplot(laTopicsDF.hr, aes(time, score)) + 
  geom_smooth(method = "loess", span = 0.1)
grid.arrange(la1, la2, ncol = 1)
